Reanalysis Step 7: Missingness Pattern Analysis

### 2025-09-01 reanalysis-7-missingness_patterns.qmd
fix ai idiiocy

# Convert to data frame format
# ExtractSmd returns a list where each element is the SMD for a variable
smd_values <- unlist(smd_raw[1:(length(smd_raw)-1)])  # Exclude the Variable element
variable_names <- names(smd_values)

smd_data <- data.frame(
  Variable = variable_names,
  SMD = smd_values,
  stringsAsFactors = FALSE
)

>>>>

# ExtractSmd returns a list - extract just the numeric SMD values
# The list has one element per variable, plus a "Variable" element with names
if (is.list(smd_raw) && "Variable" %in% names(smd_raw)) {
  # Get variable names from the Variable element
  var_names <- smd_raw$Variable
  # Get SMD values (all elements except Variable)
  smd_values <- unlist(smd_raw[names(smd_raw) != "Variable"])

  smd_data <- data.frame(
    Variable = var_names,
    SMD = smd_values,
    stringsAsFactors = FALSE
  )
} else if (is.data.frame(smd_raw)) {
  # If it's a data frame, use rownames as variable names
  smd_data <- data.frame(
    Variable = rownames(smd_raw),
    SMD = smd_raw[, 1],
    stringsAsFactors = FALSE
  )
} else {
  # Fallback: use available_vars as variable names
  smd_values <- unlist(smd_raw)
  smd_values <- smd_values[!is.na(suppressWarnings(as.numeric(smd_values)))]

  smd_data <- data.frame(
    Variable = available_vars[1:length(smd_values)],
    SMD = as.numeric(smd_values),
    stringsAsFactors = FALSE
  )
}
